\section{Addressing}

IP addressing is crucially important for any Internet service. Indeed
with the current arrangement on the West Coast, where several networks
are sharing a small number of IP addresses -- in some cases just a
single one -- amongst their users, the case can be made that they are
not providing Internet access at all. There might be some hyperbole in
that statement, but not much.

Here are some reasons why IP addresses are important and using address
translation is not desireable:
\begin{itemize}
  \item Bad behaviour by one individual -- purposeful or accidental --
    and the reaction of others on the Internet affects everyone who is
    sharing the same address. Concretely, Google may stop answering
    search queries from the entire network because it thinks that it
    is one computer infected by a virus.
  \item Tracking usage to its source is very difficult. This is
    because of the information loss at the border where address
    translation happens. This means that it is not easily possible to
    notify the relevant user or take whatever action is necessary in
    case of complaints or legal action.
  \item While looking at web sites may work, other things that one
    might want to use the Internet for can break in a variety of
    ways. Particularly susceptible to this are VoIP (internet
    telephony) and GSM mobile pico-cells.
  \item Running services is not possible. Perhaps someone wants to run
    a web server to serve images from their camera looking at the
    beautiful scenery, or run an ssh server so that they can connect
    to their home computer while they are away elsewhere. Perhaps some
    parts of the network need to be instrumented and monitored, or
    data from a weather station or electricity generation system
    collected. These things are possible but very difficult without IP
    addresses.
\end{itemize}

Though IPv4 addresses are scarce and becoming difficult to obtain, it
is still possible for a new Internet Service Provider to obtain
them. This means joining the RIPE internet registry, and only one
new block of IPv4 addresses will be allocated -- a /22 network which
contains 1024 addresses. As a member of RIPE it is also possible to
purchase or lease additional addresses on the open market at a cost in
the neighbourhood of \pounds 10-20 at the time of writing.

Joining RIPE has a cost \cite{RIPECharges}. The sign-up fee is \euro
2000. Then there is an ongoing yearly membership fee of \euro 1750
plus \euro 50 per address block.

It is a requirement for obtaining IPv4 addresses to also implement
IPv6.
